\papertitle

### 2021-03-09 source_separation/paper/paper.tex
Improve OpenUnmix description

@@

			\subsubsection{OpenUnmix}
			Open-Unmix~\cite{open-unmix} is based on a bidirectional LSTM model from~\cite{Uhlich2017}. It is an open-source implementation of a musical source separation system. It takes as input the Short-Time Fourier Transform of the input signal.

>>>>

			\subsubsection{OpenUnmix}
			Open-Unmix~\cite{open-unmix} is an open source implementation of a deep music source separation model, based on \cite{Uhlich207}. It is actually composed of multiple models that are trained for each target (such as 'vocals', 'drums', ...). Each of these models is trained on the specific target using the same architecture, based on a three layer bidirectionnal LSTM network. Open-Unmix operates on the Short Time Fourier Transform of the input mixture, which is first standardized. It predicts the target by multiplying the output of the LSTM network with the magnitude spectogram of the input, essentially applying a mask. Open-Unmix also use Wiener filtering as a last processing step.

@@
